\plaintitle

### 2017-04-26 statistical-quorum.tex
TODOs.

@@

>>>>

PeerMind source code is available under open source licence at \url{http://redacted.for.blind.review} and
anonymized dataset of interactions with the app is available at \url{http://redacted.for.blind.review}.

@@

\todo[inline]{More work on security evaluation of potential attacks when a community is using statistical quorum to force a decision.
Is there a game theoretical approach to it?}

\todo[inline]{How to surface information about credibility to users better than just a number? Visualizations? How can we help them
understand what exactly this is and how the math works?}
